---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PairwiseEucleadianDistance

<!-- badges: start -->
This is a minimal working example of my first R Package for STAT545!
<!-- badges: end -->

The goal of PairwiseEucleadianDistance is to calculate a matrix of pairwise Euclidean distances between two inputs. Each input can be a numeric vector, treated as one dimensional points, or a numeric matrix or data frame with rows as points and columns as features or dimensions. Make sure that the number of columns (dimensions) match.


## Installation

You can install the development version of PairwiseEucleadianDistance from [GitHub](https://github.com/stat545ubc-2025/Pairwise-Eucleadian-Distance) with:

``` r
# install.packages("devtools")
devtools::install_github("Parsa2018/Pairwise-Eucleadian-Distance")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PairwiseEucleadianDistance)
## basic example code
X <- rbind(c(0, 0), c(1, 5), c(2, 0))
Y <- rbind(c(0, 1), c(2, 4))
pairwise_euclid(X, Y)
```

